Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-04-30 tex/ms.tex
start on sampling description, move some text in results around

We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta, \lambda(1+z)) & = &
\frac{m_*}{4\pi d_L^2(1+z)} G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) e^ {-k_\lambda\tau_V} 
\\ 
\theta & \equiv & [m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta]
\quad ,
\end{eqnarray} where the parameters $\theta$ include include the age
$t$, metallicity $Z$, stellar mass $m_*$, dust attenuation effective
$V$-band optical depth $\tau_V$, velocity dispersion $\sigma_v$,
luminosity distance $d_L$ and redshift $z$.  The spectrum of one solar
mass of stars that formed at time $t$ with metallicity $Z$ is given by
$S(\lambda, t, Z [, \beta])$ where the additional parameters $\beta$
may include details of the population synthesis, such as the IMF slope
and adjustments to the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (DO WE WANT TO
VARY IMF SLOPE?).  We will also fix the shape of the attenuation
curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ and assume that $d_L$ is
known to high accuracy from independent methods.

@@

@@

To demonstrate the effectiveness of our spectrophotometric calibration
strategy we will infer the parameters $\theta$ from the spectrum both
\emph{before} and \emph{after} it has been spectrophotometrically
calibrated using typical techniques and ancillary spectrophotometric
calibration data. (PROBABLY NEED WORDS FROM NELSON HERE, OR CITE HIS
PAPER IF DETAILED ENOUGH)

>>>>

To demonstrate the effectiveness of our spectrophotometric calibration
strategy we will infer the parameters $\theta$ from the spectrum both
\emph{before} and \emph{after} it has been spectrophotometrically
calibrated using typical techniques and ancillary spectrophotometric
calibration data. ( CITE NC)

We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta, \lambda(1+z)) & = &
\frac{m_*}{4\pi d_L^2(1+z)} G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) e^ {-k_\lambda\tau_V} 
\\ 
\theta & \equiv & [m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta]
\quad ,
\end{eqnarray} where the parameters $\theta$ include include the age
$t$, metallicity $Z$, stellar mass $m_*$, dust attenuation effective
$V$-band optical depth $\tau_V$, velocity dispersion $\sigma_v$,
luminosity distance $d_L$ and redshift $z$.  The spectrum of one solar
mass of stars that formed at time $t$ with metallicity $Z$ is given by
$S(\lambda, t, Z [, \beta])$ where the additional parameters $\beta$
may include details of the population synthesis, such as the IMF slope
and adjustments to the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} and assume that $d_L$ is known to high
accuracy from independent methods.

@@

BDJ WORDS ABOUT FSPS.

@@

Our sampling of the posterior is accomplished using \texttt{emcee}
\cite{dfm} after an intial round of minimization.
